---
params:
  Country: ASEAN
geometry: "left=1cm,right=1cm,top=1.5cm,bottom=2cm"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fancyhdr}
# - \usepackage{unicode-math}
# - \usepackage{fontspec}
# - \setmainfont{"BCSans"}
# - \setmainfont{BCSans}
# - \setmainfont{Arial}
output:
  pdf_document: 
    # keep_tex:  true
    # latex_engine: xelatex
    includes:
      in_header: columns.tex
  html_document: default
pagetitle: Country Trade Profiles
---
<!--
Copyright 2024 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)

## need "html" so that formatting shows up (e.g., colorize function)
options(knitr.table.format = function() {
  if (knitr::is_latex_output()) "latex" else "html"
})

## need to escape '&' in "China & Hong Kong", else PDF crashes, (but not for html code)
knitr::knit_hooks$set(inline = function(x) {
  if(knitr::is_latex_output()) {
    return(gsub(pattern = "&", 
              replacement = "\\&", 
              x = x, 
              fixed = TRUE))
  } else {
    x
  }
})

# this doesn't seem to work
# ## trying to get fontspec & setmainfont to work
# tempsty <- file.path(tempdir(), "unicode-math.sty")
# file.copy("unicode-math.sty", tempsty, overwrite = TRUE)
# tempxesty <- file.path(tempdir(), "unicode-math-xetex.sty")
# file.copy("unicode-math-xetex.sty", tempxesty, overwrite = TRUE)
# tempxesty1 <- file.path(tempdir(), "unicode-math-table.tex")
# file.copy("unicode-math-table.tex", tempxesty1, overwrite = TRUE)
# tempxesty2 <- file.path(tempdir(), "unicode-math-luatex.sty")
# file.copy("unicode-math-luatex.sty", tempxesty, overwrite = TRUE)

```

```{r make_tables, include = FALSE}

### * page 1 source note for countries, for Tables 4 & 5
source_pg1 <- c("Data Source: International Trade Centre")
## no longer the case (2024)
# if(params$Country == "United States") {
#   source_pg1 <- c("Data Source: US Census Bureau")
# }


### * Page 1 tables ----

## Table 1: Top 5 BC Origin Exports to params$Country, 2019
new_title <- paste0("Top 5 BC Origin Exports to ", params$Country, ", ", 
                    years$year[years$tab == "yearSC"])

t01d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t01) %>%
  unnest(cols = c(t01)) %>%
  rename({{new_title}} := Commodity) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`Cdn $Millions` = case_when(str_detect(`Cdn $Millions`, "[.]") ~ `Cdn $Millions`,
                                     TRUE ~ paste0(`Cdn $Millions`, ".0")))
t01 <- format.for.html(tab = t01d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
    column_spec(1, width = "18em")


## Table 2: Top 5 Canadian Exports to params$Country, 2019
new_title <- paste0("Top 5 Canadian Exports to ", params$Country, ", ", 
                    years$year[years$tab == "yearSC"])

t02d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t02) %>%
  unnest(cols = c(t02)) %>%
  rename({{new_title}} := Commodity) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`Cdn $Millions` = case_when(str_detect(`Cdn $Millions`, "[.]") ~ `Cdn $Millions`,
                                     TRUE ~ paste0(`Cdn $Millions`, ".0")))

t02 <- format.for.html(tab = t02d, alignVector = c("l", "c", "c"), boldRow = 6)


## Table 3: Top 5 Canadian Imports from params$Country, 2019
new_title <- paste0("Top 5 Canadian Imports from ", params$Country, ", ", 
                    years$year[years$tab == "yearSC"])

t03d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t03) %>%
  unnest(cols = c(t03)) %>%
  rename({{new_title}} := Commodity) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`Cdn $Millions` = case_when(str_detect(`Cdn $Millions`, "[.]") ~ `Cdn $Millions`,
                                     TRUE ~ paste0(`Cdn $Millions`, ".0")))
t03 <- format.for.html(tab = t03d, alignVector = c("l", "c", "c"), boldRow = 6)


## Table 4: Top 5 Exports from params$Country to the Rest of the World, 2018
new_title <- paste0("Top 5 Exports from ", params$Country, " to the Rest of the World, ",
                    years$year[years$tab == "yearITC"])
if(params$Country %in% grpdCountries) {  new_title <- paste0(new_title, "*")  }

t04d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t04) %>%
  unnest(cols = c(t04)) %>%
  rename({{new_title}} := var) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`US $Millions` = case_when(str_detect(`US $Millions`, "[.]") ~ `US $Millions`,
                                     TRUE ~ paste0(`US $Millions`, ".0")))
t04 <- format.for.html(tab = t04d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
  #footnote(general = "Data Source: International Trade Centre", general_title = "")
  footnote(general = source_pg1, general_title = "")


## Table 5: Top 5 Imports into params$Country from the Rest of the World, 2018
new_title <- paste0("Top 5 Imports into ", params$Country, " from the Rest of the World, ",
                    years$year[years$tab == "yearITC"])
if(params$Country %in% grpdCountries) {  new_title <- paste0(new_title, "*")  }

t05d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t05) %>%
  unnest(cols = c(t05)) %>%
  rename({{new_title}} := var) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`US $Millions` = case_when(str_detect(`US $Millions`, "[.]") ~ `US $Millions`,
                                     TRUE ~ paste0(`US $Millions`, ".0")))
t05 <- format.for.html(tab = t05d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
  #footnote(general = "Data Source: International Trade Centre", general_title = "")
  footnote(general = source_pg1, general_title = "")


## Table 6: Provincial Distribution of Exports to params$Country, 2019
new_title <- paste0("Provincial Distribution of Exports to ", params$Country, ", ", 
                    years$year[years$tab == "yearSC"])

t06d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t06) %>%
  unnest(cols = c(t06)) %>%
  ## add '.0' to numbers with no decimal showing
  mutate(`Cdn $Millions` = case_when(str_detect(`Cdn $Millions`, "[.]") ~ `Cdn $Millions`,
                                     TRUE ~ paste0(`Cdn $Millions`, ".0")))
BCrow_cty <- which(str_detect(t06d$`Province of Origin`, "British Columbia"))
t06d <- t06d %>%
  rename({{new_title}} := `Province of Origin`)
t06 <- format.for.html(tab = t06d, alignVector = c("l", "c", "c"), boldRow = 14) %>%
  row_spec(BCrow_cty, bold = TRUE)


### * additional note for Tables 4 & 5 for grouped countries ----
if(params$Country %in% grpdCountries) {
  if(str_detect(params$Country, "China"))    {  groups <- paste0("China and Hong Kong") }
  if(str_detect(params$Country, "UK"))       {  groups <- paste0("European Union countries") }
  if(str_detect(params$Country, "European")) {  groups <- paste0("European Union countries") }
  if(params$Country == "ASEAN")              {  groups <- paste0("ASEAN countries") }
  note_grp <- paste0("*", params$Country, " export and import data include trade between ", groups, ".")
} else {
  note_grp <- ""
}


### * Page 2 tables ----

## Table 7: params$Country General Information
t07_title <- paste0(params$Country, " General Information")

t07d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t07) %>%
  unnest(cols = c(t07))
t07 <- t07d %>%
  mutate(Var = case_when(## table prints on a single line (wrong) UNLESS escape = TRUE in kable() below
                         Var == "GDP (US$ billions)*" ~ "GDP (US\\$ billions)*",
                         Var == "Per Capita GDP (US$ 2017)*" ~ "Per Capita GDP (US\\$ 2017)*",
                         TRUE ~ as.character(Var))) %>%
  kbl(align = c("l", "r", "c"), escape = TRUE, col.names = c("", "", "")) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "10em") %>%
  #footnote(general = "*Purchasing Power Parity \n Source: CIA", general_title = "")
  footnote(general = source_pg2[1:2], general_title = "")

           
## Table 8: BC's High Technology Trade with params$Country (Cdn$ Millions)
t08_title <- paste0("BC's High Technology Trade with ", params$Country, " (Cdn\\$ Millions)")
t08_title_xlsx <- paste0("BC's High Technology Trade with ", params$Country, " (Cdn$ Millions)")

t08d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t08) %>%
  unnest(cols = c(t08)) %>%
  ## convert to dollars (in millions), add (if needed) comma separator
  mutate(`Domestic Exports` = scales::dollar(`Domestic Exports`, scale = 0.000001, big.mark = ","),
         `Re-Exports` = scales::dollar(`Re-Exports`, scale = 0.000001, big.mark = ","),
         `Imports` = scales::dollar(`Imports`, scale = 0.000001, big.mark = ","),
         `Trade Balance` = scales::dollar(`Trade Balance`, scale = 0.000001, big.mark = ","))
t08 <- format.for.html.footnote(tab = t08d, alignVector = c("l", "c", "c", "c", "c"), 
                                footNote = source_pg2[3])
  # footnote(general = "Source: BC Stats", general_title = "")


## Table 9: Canada's Investment Position with params$Country (Cdn$ Millions)
t09_title <- paste0("Canada's Investment Position with ", params$Country, " (Cdn\\$ Millions)")
t09_title_xlsx <- paste0("Canada's Investment Position with ", params$Country, " (Cdn$ Millions)")
new_col1 <- paste0("Canadian Direct Investment in ", params$Country)
new_col2 <- paste0("Direct Investment in Canada by ", params$Country)

t09d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t09) %>%
  unnest(cols = c(t09)) %>%
  filter(Year >= max(as.numeric(Year))-9) %>%
  ## convert to dollars, add (if needed) comma separator
  mutate(`Canadian Direct Investment` = 
           case_when(`Canadian Direct Investment` == "x" ~ "x",
                     `Canadian Direct Investment` == ".." ~ "..",
                     TRUE ~ scales::dollar(as.numeric(`Canadian Direct Investment`))),
         `Direct Investment in Canada` = 
           case_when(`Direct Investment in Canada` == "x" ~ "x",
                     `Direct Investment in Canada` == ".." ~ "..",
                     TRUE ~ scales::dollar(as.numeric(`Direct Investment in Canada`)))) %>%
rename({{new_col1}} := `Canadian Direct Investment`,
         {{new_col2}} := `Direct Investment in Canada`)
t09 <- format.for.html.footnote(tab = t09d, alignVector = c("l", "c", "c"),
                                footNote = source_pg2[4])
                                #footNote = "Source: Statistics Canada")
rm(new_col1, new_col2)


## Table 10: Travellers from params$Country Entering Canada Through BC and Immigration to BC from params$Country
t10_title <- paste0("Travellers from ", params$Country, " Entering Canada Through BC and Immigration to BC from " , params$Country)

t10d <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t10) %>%
  unnest(cols = c(t10)) %>%
  filter(Year >= max(as.numeric(Year))-9) %>%
  mutate(`Travellers (Persons)` = prettyNum(`Travellers (Persons)`, big.mark = ","),
         `Immigrants (Persons)` = prettyNum(`Immigrants (Persons)`, big.mark = ","))
t10 <- format.for.html.footnote(tab = t10d, alignVector = c("l", "c", "c"), 
                                footNote = source_pg2[5:7])
                                # footNote = "Sources: \n Travellers - Statistics Canada \n Immigrants - Immigration, Refugees and Citizenship Canada")


```

```{r make_charts, include = FALSE}

## Chart 1: BC Origin Exports to params$Country
##       blue bars = $Millions, t11 `BC Exports`
##       line = share, t11 `BC Exports` / t11 `Canada Exports`
chart1 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t11) %>%
  c1(country = params$Country, nested = TRUE)
ggsave("chart1.png", dev = "png", width = 5, height = 3.5, units = "in")
c1_title <- paste0("BC Origin Exports to ", params$Country)


## Chart 2: Canada's Balance of Trade in Goods with params$Country
##       blue bars = Exports, t11 `Canada Exports`
##       gray bars = Imports, t11 `Canada Imports`
##       line = Balance of Trade, t11 `Trade Balance`
chart2 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t11) %>%
  c2(country = params$Country, nested = TRUE)
ggsave("chart2.png", dev = "png", width = 5, height = 3.5, units = "in")
c2_title <- paste0("Canada's Balance of Trade in Goods with ", params$Country)


## Chart 3: Canada's Balance of Trade in Services with params$Country
##       blue bars = Exports, t12 `Service Exports` (in $M)
##       gray bars = Imports, t12 `Service Imports` (in $M)
##       line = Balance of Trade, t12 `Service Trade Balance`
## ** NOTE: c3 should NOT appear when data is unavailable (i.e., when Index$X8 == "XX") **

chart3 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t12)
## if t12 is NULL, get blank "chart" to "display"
if(is.null(chart3$t12[[1]])) { 
  ##https://stackoverflow.com/questions/55537068/how-to-create-and-save-a-1x1-pixel-transparent-png-using-r
  png::writePNG(array(0, dim = c(1,1,4)), "chart3.png")
  c3_title <- c(" ")
  show_c3 <- FALSE
} else { 
  chart3 <- chart3 %>% c3(country = params$Country, nested = TRUE)
  ggsave("chart3.png", dev = "png", width = 5, height = 3.5, units = "in")
  c3_title <- paste0("Canada's Balance of Trade in Services with ", params$Country)
  show_c3 <- TRUE
}


## Chart 4: Year-over-Year % Growth in GDP of params$Country
##       line = % change, t13 value
chart4 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t13) %>%
  c4(country = params$Country, nested = TRUE, source_text = "Source: International Monetary Fund")
ggsave("chart4.png", dev = "png", width = 5, height = 3.5, units = "in")
c4_title <- paste0("Year-Over-Year \\% Growth in GDP of ", params$Country)
c4_title_xlsx <- paste0("Year-Over-Year % Growth in GDP of ", params$Country)


## Chart 5: Immigrants to BC from params$Country
##       line = Persons, t10 `Immigrants (Persons)`
chart5 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t10) %>%
  c5(country = params$Country, nested = TRUE)
ggsave("chart5.png", dev = "png", width = 5, height = 3.5, units = "in")
c5_title <- paste0("Immigrants to BC from ", params$Country)


## Chart 6: Travellers from params$Country Entering Through BC
##       line = Thousands, t10 `Travellers (Persons)`
chart6 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(Country, t10) %>%
  c6(country = params$Country, nested = TRUE)
ggsave("chart6.png", dev = "png", width = 5, height = 3.5, units = "in")
c6_title <- paste0("Travellers from ", params$Country, " Entering Canada Through BC")


```

```{r make_text, include = FALSE}

## How important is params$Country to BC and Canada?
text1_title <- paste0("How important is ", params$Country, " to BC and Canada?")

t15 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t15) %>%
  unnest(cols = c(t15))

if (!(params$Country %in% c("ASEAN", "EU + UK", "China & Hong Kong", "European Union"))) {
  text1 <- paste0(params$Country,
                 " ranked #",
                 t15$Rank[t15$Var == "BC Exports"], 
                 " as a destination for BC origin exports in ",
                 years$year[years$tab == "yearSC"],
                 " with ",
                 t15$Perc[t15$Var == "BC Exports"],
                 " of BC's commodity exports shipped there. It was ranked #",
                 t15$Rank[t15$Var == "Canada Exports"],
                 " as a destination for Canadian exports with ",
                 t15$Perc[t15$Var == "Canada Exports"],
                 " of Canadian goods exports shipped there and #",
                 t15$Rank[t15$Var == "Canada Imports"],
                 " as a source of imports into Canada with ",
                 t15$Perc[t15$Var == "Canada Imports"],
                 " of Canadian imports originating from ",
                 params$Country,
                 ".")
}

if (params$Country %in% c("ASEAN", "EU + UK", "China & Hong Kong", "European Union")) {
  text1 <- paste0(params$Country,
                 " was the destination for ",
                 t15$Perc[t15$Var == "BC Exports"],
                 " of BC's commodity exports shipped in ",
                 years$year[years$tab == "yearSC"],
                 ". Nationally, ",
		 t15$Perc[t15$Var == "Canada Exports"],
		 " of Canadian goods exports were shipped to ",
            	 params$Country,
		 ", while ",
		 t15$Perc[t15$Var == "Canada Imports"],
		 " of Canadian imports originated from ",
		 params$Country,
                 ".")
}
		 


## How important is Canada to params$Country?
text2_title <- paste0("How important is Canada to ", params$Country, "?")

t16 <- nested_data_countries %>%
  filter(Country == params$Country) %>%
  select(t16) %>%
  unnest(cols = c(t16)) %>%
  mutate(Share = janitor::round_half_up(Share, digits = 1))

text2 <- paste0("Canada was the source of approximately ",
                # janitor::round_half_up(t16$Share[t16$Var == "Imports into Canada"], digits = 1),
                t16$Share[t16$Var == "Imports into Canada"],
                "% of imports into ",
                params$Country,
                " in ",
                years$year[years$tab == "yearITC"],
                ". Approximately ",
                # janitor::round_half_up(t16$Share[t16$Var == "Exports from Canada"], digits = 1),
                t16$Share[t16$Var == "Exports from Canada"],
                "% of exports from ",
                params$Country,
                " were destined for Canada in that year.")

```

```{r, include = knitr::is_latex_output()}
## The LaTeX environment `tiny` is only generated for LaTeX output.
# knitr::asis_output('\n\n\\begin{tiny}')
## It actually shows \begin{tiny} in PDF. It runs fine without this code...
```

<!-- page 1 -->
```{=latex}
\pagestyle{fancy}
\setlength\headheight{29pt}
\fancyhead[L]{\fontsize{20}{22} \selectfont {\textbf{Fact Sheet}}}
\fancyhead[R]{\fontsize{20}{22} \selectfont {\textbf{`r colorize(toupper(params$Country), color = '#2A64AB')`}}}
\fancyfoot[L]{BC Stats}
\fancyfoot[C]{www.bcstats.gov.bc.ca}
\fancyfoot[R]{Data last updated: `r last_update`}
\renewcommand{\headrule}{\vbox to 0pt{\hbox to\headwidth{\dotfill}\vss}}

\begin{cols}
\begin{col}{0.52\textwidth}
\vspace{-20pt}
```
<!-- :::::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.52\textwidth}"} -->
```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf(tab = t01d, alignVector = c("l", "c", "c"), boldRow = 6) #%>%
  # footnote(general = "", general_title = "")  ## add blank line after table
format.for.pdf(tab = t02d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t03d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t04d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
  footnote(general = c(source_pg1), general_title = "")
format.for.pdf(tab = t05d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t06d, alignVector = c("l", "c", "c"), boldRow = 14) %>%
  row_spec(BCrow_cty, bold = TRUE)
```

```{=html}
<table>
  <tr>
    <td width = "52%">
      <h1><strong>Fact Sheet</strong></h1></br>
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t01
t02
t03
t04
t05
```

```{=latex}
\end{col}
\begin{col}{0.02\textwidth}
~
\end{col}
\begin{col}{0.46\textwidth}
\vspace{-20pt}
```
<!-- ::: -->
<!-- ::: {.col data-latex="{0.02\textwidth}"} -->
<!-- \  -->
<!-- ::: -->
<!-- ::: {.col data-latex="{0.46\textwidth}"} -->
```{=html}
</td>
<td width = "2%">&nbsp;&nbsp;</td>
<td width = "46%", valign = "top"><span style = 'color: #2A64AB";'>
  <h1><strong><center>`r colorize(toupper(params$Country), color = '#2A64AB')`</center></strong></h1></br>
```

`r bold.center.color.text(c1_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
## original width = 5, height = 3.5;  90% is 4.5 X 3.15;  80% is 4 X 2.8
chart1
```

```{=latex}
\vspace{-10pt}
```

`r bold.center.color.text(c2_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart2
```

```{=latex}
\vspace{-10pt}
```

`r bold.center.color.text(c3_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
if(show_c3 == TRUE) { chart3 }
```

```{=html}
<br><br><br><br><br>
```

```{=latex}
\fontsize{7.5}{9.5}\selectfont
\vspace{-5pt}
```

`r note_grp`

```{=html}
    </td>
  </tr>
  <tr>
    <td width = "52%">
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
## for html, put t06 in own row with text1 and text2
t06
```

```{=html}
    </td>
    <td width = "2%">&nbsp;&nbsp;</td>
    <td width = "46%", valign = "top">
```

```{=latex}
\fontsize{7.5}{9.5}\selectfont
\vspace{-5pt}
```

**`r colorize(text1_title, color = "#2A64AB")`**   
`r text1`

**`r colorize(text2_title, color = "#2A64AB")`**   
`r text2`

```{=html}
<br><br><br><br><br><br><br><br><br><br>
```

Unless otherwise indicated, data source is Statistics Canada.  

<!-- ::: -->
<!-- :::::: -->
```{=latex}
\end{col}
\end{cols}
```

```{=html}
    </td>
  </tr>
</table>
```


<!-- page 2 -->
```{=html}
<table>
  <tr>
    <td width = "52%">
```

```{=latex}
\begin{cols}
\begin{col}{0.52\textwidth}
\vspace{-25pt}
```
<!-- :::::: {.cols data-latex=""} -->
<!-- ::: {.col data-latex="{0.52\textwidth}"} -->

**`r colorize(t07_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
t07d %>%
  kbl(align = c("l", "r", "c"), escape = TRUE, col.names = NULL, booktabs = TRUE) %>%
  ## col.names = NULL removes header row
  column_spec(1, bold = TRUE) %>%
  kable_styling(full_width = FALSE, position = "left", font_size = 6.4, latex_options = "striped") %>%
  footnote(general = c(source_pg2[1:2], ""), general_title = "")
  #footnote(general = c("*Purchasing Power Parity", "Source: CIA", ""), general_title = "")
## include blank footnote at end to add space between this table and next table in PDF
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t07
```

**`r colorize(t08_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf.footnote(tab = t08d, alignVector = c("l", "c", "c", "c", "c"),
                        footNote = c(source_pg2[3], ""))
                        #footNote = c("Source: BC Stats", ""))
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t08
```

**`r colorize(t09_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf.footnote(tab = t09d, alignVector = c("l", "c", "c"), 
                        #footNote = c("Source: Statistics Canada", "")) 
                        footNote = c(source_pg2[4], "")) %>%
  column_spec(2:3, width = "15em")
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t09
```

**`r colorize(t10_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf.footnote(tab = t10d, alignVector = c("l", "c", "c"),
                        # footNote = c("Sources:",    "Travellers - Statistics Canada", 
                        #              "Immigrants - Immigration, Refugees and Citizenship Canada"))
                        footNote = source_pg2[5:7]) %>%
  column_spec(2:3, width = "15em")
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t10
```
<!-- ::: -->
<!-- ::: {.col data-latex="{0.02\textwidth}"} -->
<!-- \  -->
<!-- ::: -->
<!-- ::: {.col data-latex="{0.46\textwidth}"} -->
```{=latex}
\end{col}
\begin{col}{0.02\textwidth}
~
\end{col}
\begin{col}{0.46\textwidth}
\vspace{-15pt}
```

```{=html}
</td>
<td width = "2%">&nbsp;&nbsp;</td>
<td width = "46%", valign = "top">
```

`r bold.center.color.text(c4_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart4
```

`r bold.center.color.text(c5_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart5
```

`r bold.center.color.text(c6_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart6
```
<!-- ::: -->

<!-- :::::: -->
```{=latex}
\end{col}
\end{cols}
```

```{=html}
    </td>
  </tr>
</table>
```

```{r, include = knitr::is_latex_output()}
# knitr::asis_output('\\end{tiny}\n\n')
```

```{r make_xlsx, include = FALSE, eval = knitr::is_html_output()}

### * set rows for Page2 (dynamic)
## Page2 rows (based on previous tables' number of rows, in case table rows change)
row_t07 <- 1 + 1 + 1                        ## number of rows in above + col row + blank row between
row_t08 <- row_t07 + dim(t07d)[1] + 1 + 2 + 1    ## number of rows in above + col row + 2 source rows + blank row between
row_t09 <- row_t08 + dim(t08d)[1] + 1 + 1 + 1 + 1 ## rows above + title + col row + 1 source + blank row between
row_t10 <- row_t09 + dim(t09d)[1] + 1 + 1 + 1 + 1          ## as above
rows_title_p2 <- c(row_t07, row_t08, row_t09, row_t10)     ## text title above each table
rows_headers_p2 <- rows_title_p2[-1] + 1                   ## header rows for tables 8-10
rows_source_p2 <- c(row_t08 - 3, row_t08 - 2, row_t09 - 2, row_t10 - 2, (row_t10 + dim(t10d)[1]) + 2:4)  ## "Source" rows
rows_blank_p2 <- rows_source_p2[c(2, 3, 4, 7)] + 1         ## blank rows
rows_page2 <- max(rows_blank_p2)                           ## number of rows in page2


### * create empty workbook and add sheets
wb <- createWorkbook()
addWorksheet(wb, sheet = "Page1")
addWorksheet(wb, sheet = "Page2")


### * Page 1

## add styled title
writeData(wb, sheet = "Page1", x = "Fact Sheet", startRow = 1, withFilter = FALSE)
addStyle(wb, sheet = "Page1", style = sTitle, rows = 1, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page1", x = toupper(params$Country), startRow = 1, startCol = 5)
addStyle(wb, sheet = "Page1", style = sCountry, rows = 1, cols = 5, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sBorder, rows = 1, cols = 1:5, stack = TRUE)

## add styled tables
add.table.styled(wb = wb, sheet = "Page1", table = t01d, row = row_t01, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t02d, row = row_t02, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t03d, row = row_t03, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t04d, row = row_t04, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t05d, row = row_t05, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t06d, row = row_t06, style = sBlue)
addStyle(wb, sheet = "Page1", style = sBold, rows = row_t06+BCrow_cty, cols = 1:3, stack = TRUE)
## bold total rows
for(i in seq_along(rows_total_p1)) {
  addStyle(wb, sheet = "Page1", style = sBold, rows = rows_total_p1[i], cols = 1:3, stack = TRUE)
}

## add source rows
for (i in seq_along(rows_source_p1)) {
  writeData(wb, sheet = "Page1", x = source_pg1, startRow = rows_source_p1[i])
  addStyle(wb, sheet = "Page1", style = sSource, rows = rows_source_p1[i], cols = 1, stack = TRUE)
}

## add charts with titles
add.chart.titled(wb = wb, sheet = "Page1", c_title = c1_title, chart = "chart1.png", row = row_t01, col = 5)
add.chart.titled(wb = wb, sheet = "Page1", c_title = c2_title, chart = "chart2.png", row = 14, col = 5)
if(show_c3 == TRUE) {
  add.chart.titled(wb = wb, sheet = "Page1", c_title = c3_title, chart = "chart3.png", row = 27, col = 5)
}

## additional note for Tables 4 & 5 for grouped countries
if(params$Country %in% grpdCountries) {
  writeData(wb, sheet = "Page1", x = note_grp, startRow = 42, startCol = 5)
  addStyle(wb, sheet = "Page1", style = sText, rows = 42, cols = 5, stack = TRUE)
}

## add text1 & text2 ("How important is ...?"), and data source text
writeData(wb, sheet = "Page1", x = text1_title, startRow = 44, startCol = 5)
addStyle(wb, sheet = "Page1", style = sBlue, rows = 44, cols = 5, stack = TRUE)
writeData(wb, sheet = "Page1", x = text1, startRow = 45, startCol = 5)
mergeCells(wb, sheet = "Page1", cols = 5, rows = 45:50)
addStyle(wb, sheet = "Page1", style = sText, rows = 45, cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = text2_title, startRow = 52, startCol = 5)
addStyle(wb, sheet = "Page1", style = sBlue, rows = 52, cols = 5, stack = TRUE)
writeData(wb, sheet = "Page1", x = text2, startRow = 53, startCol = 5)
mergeCells(wb, sheet = "Page1", cols = 5, rows = 53:56)
addStyle(wb, sheet = "Page1", style = sText, rows = 53, cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = "Unless otherwise indicated, data source is Statistics Canada.", startRow = 58, startCol = 5)
addStyle(wb, sheet = "Page1", style = sSource, rows = 58, cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = paste0("Data last updated: ", last_update), startRow = 59, startCol = 5)
addStyle(wb, sheet = "Page1", style = sSource, rows = 59, cols = 5, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sBorder, rows = 59, cols = 1:5, stack = TRUE)


## overall page styles
addStyle(wb, sheet = "Page1", style = sText, rows = row_t01:rows_page1, cols = 1, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sStat, rows = row_t01:rows_page1, cols = 2:3, stack = TRUE, gridExpand = TRUE)

## stretch cols and rows, freeze top row
setColWidths(wb, sheet = "Page1", cols = 1:5, widths = c(42, 10, 7, 4, 66))
setRowHeights(wb, sheet = "Page1", rows = c(2:rows_page1), heights = 29)  ## set heights
setRowHeights(wb, sheet = "Page1", rows = rows_total_p1, heights = 11)    ## "Total" rows
setRowHeights(wb, sheet = "Page1", rows = c((1+row_t06):(rows_page1-1)), heights = 12)   ## Province rows (t06d)
setRowHeights(wb, sheet = "Page1", rows = rows_source_p1, heights = 11)   ## source rows
setRowHeights(wb, sheet = "Page1", rows = rows_blank_p1, heights = 11)    ## blank rows
freezePane(wb, sheet = "Page1", firstActiveRow = 2, firstActiveCol = 1)
# ungroupColumns(wb, sheet = "Page1", cols = 1:5)


### * Page 2 ----

## overall page styles
addStyle(wb, sheet = "Page2", style = sCenter, rows = row_t07:rows_page2, cols = 1, stack = TRUE)
addStyle(wb, sheet = "Page2", style = sStat2, rows = (row_t08 +1):rows_page2, cols = 2:5, stack = TRUE, gridExpand = TRUE)

## add styled title
writeData(wb, sheet = "Page2", x = "Fact Sheet", startRow = 1, withFilter = FALSE)
addStyle(wb, sheet = "Page2", style = sTitle, rows = 1, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page2", x = toupper(params$Country), startRow = 1, startCol = 7)
addStyle(wb, sheet = "Page2", style = sCountry, rows = 1, cols = 7, stack = TRUE)
writeData(wb, sheet = "Page2", x = "Continued", startRow = 2)
addStyle(wb, sheet = "Page2", style = sContinued, rows = 2, cols = 1:7, stack = TRUE)

## fix up tables
t07d <- t07d %>%
  mutate(X1 = "", X2 = "") %>%
  select(Var, X1, X2, value, Year)

t09d <- t09d %>% mutate(` ` = "", `  ` = "")
t09d <- t09d[, c(1,2,4,3,5)]

t10d <- t10d %>% mutate(` ` = "", `  ` = "") %>%
  select(Year, `Travellers (Persons)`, ` `, `Immigrants (Persons)`, `  `)

## add styled and titled tables
writeData(wb, sheet = "Page2", x = t07_title, startRow = row_t07)
addStyle(wb, sheet = "Page2", style = sBlue, rows = row_t07, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page2", x = t07d, startRow = row_t07+1, colNames = FALSE)
for (i in 4:8) {
  mergeCells(wb, sheet = "Page2", cols = 1:3, rows = i)
}
addStyle(wb, sheet = "Page2", style = sBold, rows = 4:8, cols = 1, stack = TRUE, gridExpand = TRUE)
addStyle(wb, sheet = "Page2", style = sStat, rows = 4:8, cols = 4, stack = TRUE, gridExpand = TRUE)

add.table.styled.titled(wb = wb, sheet = "Page2", title = t08_title_xlsx, table = t08d, row = row_t08)

add.table.styled.titled(wb = wb, sheet = "Page2", title = t09_title_xlsx, table = t09d, row = row_t09)
for (i in (row_t09+1):(row_t09 + 1 + dim(t09d)[1])) {
  mergeCells(wb, sheet = "Page2", cols = 2:3, rows = i)
  mergeCells(wb, sheet = "Page2", cols = 4:5, rows = i)
}

add.table.styled.titled(wb = wb, sheet = "Page2", title = t10_title, table = t10d, row = row_t10)
mergeCells(wb, sheet = "Page2", cols = 1:5, rows = row_t10)
addStyle(wb, sheet = "Page2", style = sText, rows = row_t10, cols = 1:5, stack = TRUE)
for (i in (row_t10+1):(row_t10 + 1 + dim(t10d)[1])) {
  mergeCells(wb, sheet = "Page2", cols = 2:3, rows = i)
  mergeCells(wb, sheet = "Page2", cols = 4:5, rows = i)
}

for (i in seq_along(source_pg2)) {
  writeData(wb, sheet = "Page2", x = source_pg2[i], startRow = rows_source_p2[i])
  addStyle(wb, sheet = "Page2", style = sSource, cols = 1, rows = rows_source_p2[i])
}

## add charts with titles
add.chart.titled(wb = wb, sheet = "Page2", c_title = c4_title_xlsx, chart = "chart4.png", row = row_t07, col = 7)
add.chart.titled(wb = wb, sheet = "Page2", c_title = c5_title, chart = "chart5.png", row = 22, col = 7)
add.chart.titled(wb = wb, sheet = "Page2", c_title = c6_title, chart = "chart6.png", row = 41, col = 7)

## add Page2's bottom border
addStyle(wb, sheet = "Page2", style = sBorder, rows = 61, cols = 1:7, stack = TRUE)

## stretch cols and rows, freeze top rows
setColWidths(wb, sheet = "Page2", cols = 1:7, widths = c(6, 12, 12, 12, 12, 4, 66))
setRowHeights(wb, sheet = "Page2", rows = c(3:rows_page2), heights = 14) ## set heights
setRowHeights(wb, sheet = "Page2", rows = rows_title_p2, heights = 29)   ## title rows
setRowHeights(wb, sheet = "Page2", rows = rows_headers_p2, heights = 29) ## table header rows
setRowHeights(wb, sheet = "Page2", rows = rows_source_p2, heights = 11)  ## source rows
setRowHeights(wb, sheet = "Page2", rows = rows_blank_p2, heights = 11)   ## blank rows
freezePane(wb, sheet = "Page2", firstActiveRow = 3, firstActiveCol = 1)
# ungroupColumns(wb, sheet = "Page2", cols = 1:7)


### * save workbook ----
saveWorkbook(wb, paste0("Fact", params$Country, ".xlsx"), overwrite = TRUE)
## Copy the report file to a temporary directory before processing it, in case we don't have write permissions to the current working dir (which can happen when deployed).
tempWB <- file.path(tempdir(), paste0("Fact", params$Country, ".xlsx"))
file.copy(from = paste0("Fact", params$Country, ".xlsx"), to = tempWB, overwrite = TRUE)
rm(wb, i)

```
