---
params:
  state: Alabama
geometry: "left=1cm,right=1cm,top=1.5cm,bottom=2cm"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fancyhdr}
output:
  pdf_document: 
    # keep_tex:  true
    includes:
      in_header: columns.tex
  html_document: default
pagetitle: State Trade Profiles
---
<!--
Copyright 2024 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r setup, include = FALSE}


knitr::opts_chunk$set(echo = FALSE)

## need "html" so that formatting shows up (e.g., colorize function)
options(knitr.table.format = function() {
  if (knitr::is_latex_output()) "latex" else "html"
})

```

```{r make_tables, include = FALSE}

### * Page 1 tables ----

## Table 1: Top 5 BC Origin Exports to params$state, 2019
new_title <- paste0("Top 5 BC Origin Exports to ", params$state, ", ", 
                    yearsStates$year[yearsStates$tab == "yearSC"])

t01d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t01) %>%
  unnest(cols = c(t01)) %>%
  rename({{new_title}} := Commodity)
t01 <- format.for.html(tab = t01d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
    column_spec(1, width = "18em")


## Table 2: Top 5 Canadian Exports to params$state, 2019
new_title <- paste0("Top 5 Canadian Exports to ", params$state, ", ", 
                    yearsStates$year[yearsStates$tab == "yearSC"])

t02d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t02) %>%
  unnest(cols = c(t02)) %>%
  rename({{new_title}} := Commodity)
t02 <- format.for.html(tab = t02d, alignVector = c("l", "c", "c"), boldRow = 6)


## Table 3: Top 5 Canadian Imports from params$state, 2019
new_title <- paste0("Top 5 Canadian Imports from ", params$state, ", ", 
                    yearsStates$year[yearsStates$tab == "yearSC"])

t03d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t03) %>%
  unnest(cols = c(t03)) %>%
  rename({{new_title}} := Commodity)
t03 <- format.for.html(tab = t03d, alignVector = c("l", "c", "c"), boldRow = 6)


## Table 4: Top 5 Exports from params$state to the Rest of the World, 2018*
new_title <- paste0("Top 5 Exports from ", params$state, " to the Rest of the World, ", 
                    yearsStates$year[yearsStates$tab == "yearUS"], "*")

t04d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t04) %>%
  unnest(cols = c(t04)) %>%
  rename({{new_title}} := var)
t04 <- format.for.html(tab = t04d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
  footnote(general = source_pg1_states, general_title = "")
#   footnote(general = c("* These are origin of movement figures and may not represent origin of manufacture; data is by industry (NAICS) rather than commodity.", "Source: US Department of Commerce"), general_title = "")


## Table 5: Top 5 Imports into params$state from the Rest of the World, 2018
##   there is no Table 5 for States, only for Countries


## Table 6: Provincial Distribution of Exports to params$state, 2019
new_title <- paste0("Provincial Distribution of Exports to ", params$state, ", ", 
                    yearsStates$year[yearsStates$tab == "yearSC"])

t06d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t06) %>%
  unnest(cols = c(t06))
BCrow_state <- which(str_detect(t06d$`Province of Origin`, "British Columbia"))
t06d <- t06d %>%
  rename({{new_title}} := `Province of Origin`)
t06 <- format.for.html(tab = t06d, alignVector = c("l", "c", "c"), boldRow = 14) %>%
  row_spec(BCrow_state, bold = TRUE)


### * Page 2 tables ----

## Table 7: params$state General Information
t07_title <- paste0(params$state, " General Information")

t07d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t07) %>%
  unnest(cols = c(t07))
t07 <- t07d %>%
  mutate(Var = case_when(## table prints on a single line (wrong) UNLESS escape = TRUE in kable() below
                         Var == "GDP (Chained US$ Millions)" ~ "GDP (Chained 2017 US\\$ Millions)",
                         Var == "Real Per Capita GDP (US$)" ~ "Real Per Capita GDP (US\\$)",
                         TRUE ~ as.character(Var))) %>%
  kbl(align = c("l", "r", "c"), escape = TRUE, col.names = c("", "", "")) %>%
  kable_styling(full_width = FALSE, position = "left", bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, width = "10em") %>%
  footnote(general = c(source_pg2_states[1], ""), general_title = "")


## Table 8: BC's High Technology Trade with params$state (Cdn$ Millions)
t08_title <- paste0("BC's High Technology Trade with ", params$state, " (Cdn\\$ Millions)")

t08d <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t08) %>%
  unnest(cols = c(t08)) %>%
  ## convert to dollars (ALREADY in millions), add (if needed) comma separator
  mutate(`Domestic Exports` = scales::dollar(`Domestic Exports`, big.mark = ","),
         `Re-Exports` = scales::dollar(`Re-Exports`, big.mark = ","),
         `Imports` = scales::dollar(`Imports`, big.mark = ","),
         `Trade Balance` = scales::dollar(`Trade Balance`, big.mark = ","))
t08 <- format.for.html.footnote(tab = t08d, alignVector = c("l", "c", "c", "c", "c"), 
                                footNote = source_pg2_states[2])


## Table 9: Canada's Investment Position with params$state (Cdn$ Millions)
##   there is no Table 9 for States, only for Countries


## Table 10: Travellers from params$state Entering Canada Through BC and Immigration to BC from params$state
##   there is no Table 10 for States, only for Countries


```

```{r make_charts, include = FALSE}

## *** NOTE: chart functions c1-c6 were first made for countries, which is why they require "country" as argument, even though they are run here on states (as the variable) *** ##

## Chart 1: BC Origin Exports to params$state
##       blue bars = $Millions, t11 `BC Exports`
##       line = share, t11 `BC Exports` / t11 `Canada Exports`
chart1 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(Country = state, t11) %>%  ## rename state var as "Country" for chart function to run
  c1(country = params$state, nested = TRUE)
ggsave("chart1_state.png", dev = "png", width = 5, height = 3.5, units = "in")
c1_title <- paste0("BC Origin Exports to ", params$state)


## Chart 2: Canada's Balance of Trade in Goods with params$state
##       blue bars = Exports, t11 `Canada Exports`
##       gray bars = Imports, t11 `Canada Imports`
##       line = Balance of Trade, t11 `Trade Balance`
chart2 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(Country = state, t11) %>%  ## rename state var as "Country" for chart function to run
  c2(country = params$state, nested = TRUE)
ggsave("chart2_state.png", dev = "png", width = 5, height = 3.5, units = "in")
c2_title <- paste0("Canada's Balance of Trade in Goods with ", params$state)


## Chart 3: Canada's Balance of Trade in Services with params$state
##   there is no Chart 3 for States, only for (some) countries


## Chart 4: Year-over-Year % Growth in GDP of params$state
##       line = % change, t13 value
chart4 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(Country = state, t13) %>%  ## rename state var as "Country" for chart function to run
  unnest(cols = c(t13)) %>%
  rename(value = `Percent.Change`) %>%
  c4(country = params$state, nested = FALSE, 
     source_text = "Source: US Bureau of Economic Analysis")
ggsave("chart4_state.png", dev = "png", width = 5, height = 3.5, units = "in")
c4_title <- paste0("Year-Over-Year \\% Growth in GDP \\(Chained 2017 US$ Millions) of ", params$state)


## Chart 5: Immigrants to BC from params$state
##       line = Persons, t10 `Immigrants (Persons)`
##   there is no Chart 5 for States, only for Countries


## Chart 6: Travellers from params$state Entering Through BC
##       line = Thousands, t10 `Travellers (Persons)`
##   there is no Chart 6 for States, only for countries
##   Instead, this info for states is 2 text blurbs, not a chart, and only for some states


## Chart 7: BC's Balance of Trade in High Tech Goods with params$state
##       *** this chart is only for STATES ***
##       blue bars = Exports, t08 `Domestic Exports` + t08 `Re-Exports` 
##                            (most re-exports are 0, but not all)
##       gray bars = Imports, t08 `Imports`
##       line = Balance of Trade, t08 `Trade Balance`
chart7 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(state, t08) %>%
  c7(state = params$state, nested = TRUE)
ggsave("chart7_state.png", dev = "png", width = 5, height = 3.5, units = "in")
c7_title <- paste0("BC's Balance of Trade in High Tech Goods with ", params$state)


```

```{r make_text, include = FALSE}

### * Page 1 text ----

t15 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t15) %>%
  unnest(cols = c(t15))

## How does params$state compare with other US states?
text1_title <- paste0("How does ", params$state, " compare with other US states and regions&#42;?")

text1 <- paste0("Among the states, ",
                params$state,
                " ranked #", 
                t15$Rank[t15$Var == "BC Exports"],
                " as a destination for BC exports and #",
                t15$Rank[t15$Var == "Canada Exports"],
                " as a destination for Canadian exports. As a source of imports to Canada, it ranked #",
                t15$Rank[t15$Var == "Canada Imports"],
                " among the states.")

## How important is params$state to BC and Canada? (=text1 for countries)
text2_title <- paste0("How important is ", params$state, " to BC and Canada?")

text2 <- paste0("If ",
                params$state,
               " were a separate country, it would rank #",
               t15$RankAsCountry[t15$Var == "BC Exports"],
               " as a destination for BC origin exports in ",
               yearsStates$year[yearsStates$tab == "yearSC"],
               " with ",
               t15$Perc[t15$Var == "BC Exports"],
               " of BC's commodity exports shipped there. It would be ranked #",
               t15$RankAsCountry[t15$Var == "Canada Exports"],
               " as a destination for Canadian exports with ",
               t15$Perc[t15$Var == "Canada Exports"],
               " of Canadian goods exports shipped there and #",
               t15$RankAsCountry[t15$Var == "Canada Imports"],
               " as a source of imports into Canada with ",
               t15$Perc[t15$Var == "Canada Imports"],
               " of Canadian imports originating from ",
               params$state,
               ".")


### * Page 2 text ----
t10 <- nested_data_states %>%
  filter(state == params$state) %>%
  select(t10) %>%
  unnest(cols = c(t10))


## Commented out code below since this data needs to be removed - Ryann M.
##params$state Travel to Canada
## need `show_text3` and `text3_title` to exist as they are called later in script for creating PDFs and html
# if(is.na(t10$Stat[t10$Var == "TripsToCanada"])) {
  show_text3 = FALSE
  text3_title <- ""
# } else {
#   text3_title <- paste0(params$state, " Travel to Canada")
#   text3 <- paste0("There were ",
#                prettyNum(t10$Stat[t10$Var == "TripsToCanada"], big.mark = ","),
#                 " trips made by residents of ",
#                 params$state,
#                 " to Canada in ",
#                 t10$Stat[t10$Var == "Year"],
#                 " and they spent $Cdn ",
#                 t10$Stat[t10$Var == "SpendingInCanada"],
#                 " million while visiting. ",
#                 params$state,
#                 " ranked #",
#                 t10$Rank[t10$Var == "TripsToCanada"],
#                 " among the states in terms of the number of residents making trips to Canada.")
#   show_text3 = TRUE
# }

## Canadian Travel to params$state
## Added "##" to the code below since this data needs to be removed - Ryann M.
# if(is.na(t10$Stat[t10$Var == "TripsToState"])) {
  show_text4 = FALSE
  text4_title <- ""
# } else {
#   text4_title <- paste0("Canadian Travel to ", params$state)
#   text4 <- paste0("The number of trips by Canadians to ",
#                 params$state,
#                 " in ",
#                 t10$Stat[t10$Var == "Year"],
#                 " was ",
#                 prettyNum(t10$Stat[t10$Var == "TripsToState"], big.mark = ","),
#                 ". The total amount spent on those trips was $Cdn ",
#                 t10$Stat[t10$Var == "SpendingInState"],
#                " million. ",
#                 params$state,
#                 " ranked #",
#                 t10$Rank[t10$Var == "TripsToState"],
#                 " among the states as a destination for Canadian travellers.")
#   show_text4 = TRUE
# }


```

<!-- page 1 -->
```{=latex}
\pagestyle{fancy}
\setlength\headheight{29pt}
\fancyhead[L]{\fontsize{20}{22} \selectfont {\textbf{Fact Sheet}}}
\fancyhead[R]{\fontsize{20}{22} \selectfont {\textbf{`r colorize(toupper(params$state), color = '#2A64AB')`}}}
\fancyfoot[L]{BC Stats}
\fancyfoot[C]{www.bcstats.gov.bc.ca}
\fancyfoot[R]{Data last updated: `r last_update`}
\renewcommand{\headrule}{\vbox to 0pt{\hbox to\headwidth{\dotfill}\vss}}

\begin{cols}
\begin{col}{0.52\textwidth}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf(tab = t01d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t02d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t03d, alignVector = c("l", "c", "c"), boldRow = 6)
format.for.pdf(tab = t04d, alignVector = c("l", "c", "c"), boldRow = 6) %>%
  footnote(general = source_pg1_states, general_title = "")
## there is no t05d for states, only for countries
format.for.pdf(tab = t06d, alignVector = c("l", "c", "c"), boldRow = 14) %>%
  row_spec(BCrow_state, bold = TRUE)
```

```{=latex}
\end{col}
\begin{col}{0.02\textwidth}
~
\end{col}
\begin{col}{0.46\textwidth}
\vspace{-75pt}
```

```{=html}
<table>
  <tr>
    <td width = "52%">
      <h1><strong>Fact Sheet</strong></h1></br>
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t01
t02
t03
t04
```

```{=html}
</td>
<td width = "2%">&nbsp;&nbsp;</td>
<td width = "46%", valign = "top">
  <h1><strong><center>`r colorize(toupper(params$state), color = '#2A64AB')`</center></strong></h1></br>
```

`r bold.center.color.text(c1_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart1
```

`r bold.center.color.text(c2_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart2
```

```{=html}
    </td>
  </tr>
  <tr>
    <td width = "52%">
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
## for html, put t06 in own row with text1 and text2
t06
```

```{=html}
    </td>
    <td width = "2%">&nbsp;&nbsp;</td>
    <td width = "46%", valign = "top">
```

```{=latex}
\fontsize{8}{10}\selectfont
\hspace{1cm}
```

**`r colorize(text1_title, color = "#2A64AB")`**  
`r text1`

```{=latex}
\hspace{1cm}
```

**`r colorize(text2_title, color = "#2A64AB")`**  
`r text2`

```{=html}
<br><br><br><br><br><br><br><br><br><br>
```

```{=latex}
\hspace{5cm}
```

Unless otherwise indicated, data source is Statistics Canada.  
* US regions include unknown state, Puerto Rico, U.S. Virgin Islands, and the District of Colombia  

```{=latex}
\end{col}
\end{cols}
```

```{=html}
    </td>
  </tr>
</table>
```


<!-- page 2 -->
```{=html}
<table>
  <tr>
    <td width = "52%">
```

```{=latex}
\begin{cols}
\begin{col}{0.52\textwidth}
\vspace{-75pt}
```

**`r colorize(t07_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
t07d %>%
  kbl(align = c("l", "r", "c"), escape = TRUE, col.names = NULL, booktabs = TRUE) %>%
  ## col.names = NULL removes header row
  column_spec(1, bold = TRUE) %>%
  kable_styling(full_width = FALSE, position = "left", font_size = 6.4, latex_options = "striped") %>%
  footnote(general = c(source_pg2_states[1], "", ""), general_title = "")
## include blank footnote at end to add space between this table and next table
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t07
```

**`r colorize(t08_title, color = "#2A64AB")`**
```{=latex}
\vspace{-10pt}
```

```{r, results = 'asis', include = knitr::is_latex_output()}
## PDF-only code
format.for.pdf.footnote(tab = t08d, alignVector = c("l", "c", "c", "c", "c"),
                        footNote = c(source_pg2_states[2], "", ""))
```

```{r, results = 'asis', include = knitr::is_html_output()}
## html-only code
t08
```

```{=latex}
\fontsize{8}{10}\selectfont
```

**`r colorize(text3_title, color = "#2A64AB")`**  
```{r, results = 'asis'}
if(show_text3 == TRUE) {
  tagList(text3)
}
```

```{=latex}
\hspace{1cm}
```

**`r colorize(text4_title, color = "#2A64AB")`**  
```{r, results = 'asis'}
if(show_text4 == TRUE) {
  tagList(text4)
}
```

```{=latex}
\hspace{5cm}

\end{col}
\begin{col}{0.02\textwidth}
~
\end{col}
\begin{col}{0.46\textwidth}
```

```{=html}
</td>
<td width = "2%">&nbsp;&nbsp;</td>
<td width = "46%", valign = "top">
```

`r bold.center.color.text(c4_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart4
```

`r bold.center.color.text(c7_title, color = "#2A64AB")`
```{r, results = 'asis', fig.width = 5, fig.height = 3.5}
chart7
```

```{=latex}
\end{col}
\end{cols}
```

```{=html}
    </td>
  </tr>
</table>
```

```{r make_xlsx, include = FALSE, eval = knitr::is_html_output()}

### * set rows for Page2 (dynamic)
## Page2 rows (based on previous tables' number of rows, in case table rows change)
row_t07 <- 1 + 1 + 1                             ## number of rows in above + col row + blank row between
row_t08 <- row_t07 + dim(t07d)[1] + 1 + 1 + 1    ## number of rows in above + col row + 1 source row + blank row between
row_t08_end <- (row_t08 + dim(t08d)[1] + 2)
rows_title_p2 <- c(row_t07, row_t08)             ## text title above each table
rows_headers_p2 <- rows_title_p2[-1] + 1         ## header row for table 8
rows_source_p2 <- c(row_t08 - 2, row_t08_end)    ## "Source" rows
rows_blank_p2 <- c(rows_source_p2 + 1)           ## blank rows
if(show_text3 == TRUE) {
  row_title3 <- row_t08_end + 2                  ## end of table 8 + blank row between
  row_text3 <- row_title3 + 1                    ## 1 row after title 3
  row_text3_end <- row_title3 + 4                ## end of text 3 (spans multiple lines in merge)
  rows_title_p2 <- c(rows_title_p2, row_title3)  ## add text 3 title to title rows, if exists
  rows_blank_p2 <- c(rows_blank_p2, (row_text3_end + 1))  ## add blank after text 3, if exists
}

if(show_text4 == TRUE) {
  ## if there is a text 3 for this state
  if(show_text3 == TRUE) {
    row_title4 <- row_text3_end + 2              ## end of text3 + blank row between
  } else {
    ## if there is NOT a text 3 for this state
    row_title4 <- row_t08_end + 2                ## end of t08 (when there is no text3) + blank row between
  }
  row_text4 <- row_title4 + 1                    ## 1 row after title 4
  row_text4_end <- row_title4 + 4                ## end of text 4 (spans multiple lines in merge)
  rows_title_p2 <- c(rows_title_p2, row_title4)  ## add text 3 title to title rows, if exists
  rows_blank_p2 <- c(rows_blank_p2, (row_text4_end + 1))  ## add blank after text 4, if exists
}

rows_page2 <- 41 ## max(rows_blank_p2)           ## number of rows in page2

### * create empty workbook and add sheets
wb <- createWorkbook()
addWorksheet(wb, sheet = "Page1")
addWorksheet(wb, sheet = "Page2")


### * Page 1 ----

## add styled title
writeData(wb, sheet = "Page1", x = "Fact Sheet", startRow = 1, withFilter = FALSE)
addStyle(wb, sheet = "Page1", style = sTitle, rows = 1, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page1", x = toupper(params$state), startRow = 1, startCol = 5)
addStyle(wb, sheet = "Page1", style = sCountry, rows = 1, cols = 5, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sBorder, rows = 1, cols = 1:5, stack = TRUE)

## add styled tables
add.table.styled(wb = wb, sheet = "Page1", table = t01d, row = row_t01, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t02d, row = row_t02, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t03d, row = row_t03, style = sBlue)
add.table.styled(wb = wb, sheet = "Page1", table = t04d, row = row_t04, style = sBlue)
## states do not have a t05d
add.table.styled(wb = wb, sheet = "Page1", table = t06d, row = row_t06_states, style = sBlue)
addStyle(wb, sheet = "Page1", style = sBold, rows = row_t06_states+BCrow_state, cols = 1:3, stack = TRUE)
## bold total rows
for(i in seq_along(rows_total_p1_states)) {
  addStyle(wb, sheet = "Page1", style = sBold, rows = rows_total_p1_states[i], cols = 1:3, stack = TRUE)
}

## add source rows
source_pg1_states_merge <- c(paste0(source_pg1_states[1:2], collapse = " "), source_pg1_states[3])
for (i in seq_along(rows_source_p1_states)) {
  writeData(wb, sheet = "Page1", x = source_pg1_states_merge[i], startRow = rows_source_p1_states[i])
  addStyle(wb, sheet = "Page1", style = sSource, rows = rows_source_p1_states[i], cols = 1, stack = TRUE)
}

## add charts with titles
add.chart.titled(wb = wb, sheet = "Page1", c_title = c1_title, chart = "chart1_state.png", row = row_t01, col = 5)
add.chart.titled(wb = wb, sheet = "Page1", c_title = c2_title, chart = "chart2_state.png", row = 14, col = 5)

## add text1 & text2 ("How important is ...?"), and data source text
writeData(wb, sheet = "Page1", x = text1_title, startRow = row_t06_states, startCol = 5)
addStyle(wb, sheet = "Page1", style = sBlue, rows = row_t06_states, cols = 5, stack = TRUE)
writeData(wb, sheet = "Page1", x = text1, startRow = (row_t06_states+1), startCol = 5)
mergeCells(wb, sheet = "Page1", cols = 5, rows = (row_t06_states+1):40)
addStyle(wb, sheet = "Page1", style = sText, rows = (row_t06_states+1), cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = text2_title, startRow = 42, startCol = 5)
addStyle(wb, sheet = "Page1", style = sBlue, rows = 42, cols = 5, stack = TRUE)
writeData(wb, sheet = "Page1", x = text2, startRow = 43, startCol = 5)
mergeCells(wb, sheet = "Page1", cols = 5, rows = 43:48)
addStyle(wb, sheet = "Page1", style = sText, rows = 43, cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = "Unless otherwise indicated, data source is Statistics Canada.", startRow = rows_page1_states, startCol = 5)
addStyle(wb, sheet = "Page1", style = sSource, rows = rows_page1_states, cols = 5, stack = TRUE)

writeData(wb, sheet = "Page1", x = paste0("Data last updated: ", last_update), startRow = (rows_page1_states+1), startCol = 5)
addStyle(wb, sheet = "Page1", style = sSource, rows = (rows_page1_states+1), cols = 5, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sBorder, rows = (rows_page1_states+1), cols = 1:5, stack = TRUE)


## overall page styles
addStyle(wb, sheet = "Page1", style = sText, rows = row_t01:rows_page1_states, cols = 1, stack = TRUE)
addStyle(wb, sheet = "Page1", style = sStat, rows = row_t01:rows_page1_states, cols = 2:3, stack = TRUE, gridExpand = TRUE)

## stretch cols and rows, freeze top row
setColWidths(wb, sheet = "Page1", cols = 1:5, widths = c(42, 10, 7, 4, 66))
setRowHeights(wb, sheet = "Page1", rows = c(2:rows_page1_states), heights = 29)  ## set heights
setRowHeights(wb, sheet = "Page1", rows = rows_total_p1_states, heights = 11)    ## "Total" rows
setRowHeights(wb, sheet = "Page1", rows = c((1+row_t06_states):(rows_page1_states-1)), heights = 12)   ## Province rows (t06d)
setRowHeights(wb, sheet = "Page1", rows = rows_source_p1_states, heights = c(22, 11))   ## source rows
setRowHeights(wb, sheet = "Page1", rows = rows_blank_p1_states, heights = 11)    ## blank rows
freezePane(wb, sheet = "Page1", firstActiveRow = 2, firstActiveCol = 1)


### * Page 2 ----

## overall page styles
addStyle(wb, sheet = "Page2", style = sCenter, rows = row_t07:rows_page2, cols = 1, stack = TRUE)
addStyle(wb, sheet = "Page2", style = sStat2, rows = (row_t08 +1):rows_page2, cols = 2:5, stack = TRUE, gridExpand = TRUE)

## add styled title
writeData(wb, sheet = "Page2", x = "Fact Sheet", startRow = 1, withFilter = FALSE)
addStyle(wb, sheet = "Page2", style = sTitle, rows = 1, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page2", x = toupper(params$state), startRow = 1, startCol = 7)
addStyle(wb, sheet = "Page2", style = sCountry, rows = 1, cols = 7, stack = TRUE)
writeData(wb, sheet = "Page2", x = "Continued", startRow = 2)
addStyle(wb, sheet = "Page2", style = sContinued, rows = 2, cols = 1:7, stack = TRUE)

## fix up tables
t07d <- t07d %>%
  mutate(X1 = "", X2 = "") %>%
  select(Var, X1, X2, value, Year)

## add styled and titled tables
writeData(wb, sheet = "Page2", x = t07_title, startRow = row_t07)
addStyle(wb, sheet = "Page2", style = sBlue, rows = row_t07, cols = 1, stack = TRUE)
writeData(wb, sheet = "Page2", x = t07d, startRow = row_t07+1, colNames = FALSE)
for (i in 4:8) {
  mergeCells(wb, sheet = "Page2", cols = 1:3, rows = i)
}
addStyle(wb, sheet = "Page2", style = sBold, rows = 4:8, cols = 1, stack = TRUE, gridExpand = TRUE)
addStyle(wb, sheet = "Page2", style = sStat, rows = 4:8, cols = 4, stack = TRUE, gridExpand = TRUE)

add.table.styled.titled(wb = wb, sheet = "Page2", title = t08_title, table = t08d, row = row_t08)

for (i in seq_along(source_pg2_states)) {
  writeData(wb, sheet = "Page2", x = source_pg2_states[i], startRow = rows_source_p2[i])
  addStyle(wb, sheet = "Page2", style = sSource, cols = 1, rows = rows_source_p2[i])
}

## add text3 and text4, if exist
if(show_text3 == TRUE) {
  writeData(wb, sheet = "Page2", x = text3_title, startRow = row_title3)
  addStyle(wb, sheet = "Page2", style = sBlue, rows = row_title3, cols = 1:5, stack = TRUE)
  writeData(wb, sheet = "Page2", x = text3, startRow = row_text3)
  mergeCells(wb, sheet = "Page2", cols = 1:5, rows = row_text3:row_text3_end)
  addStyle(wb, sheet = "Page2", style = sText, rows = row_text3, cols = 1:5, stack = TRUE)
}
if(show_text4 == TRUE) {
  writeData(wb, sheet = "Page2", x = text4_title, startRow = row_title4)
  addStyle(wb, sheet = "Page2", style = sBlue, rows = row_title4, cols = 1:5, stack = TRUE)
  writeData(wb, sheet = "Page2", x = text4, startRow = row_text4)
  mergeCells(wb, sheet = "Page2", cols = 1:5, rows = row_text4:row_text4_end)
  addStyle(wb, sheet = "Page2", style = sText, rows = row_text4, cols = 1:5, stack = TRUE)
}


## add charts with titles
add.chart.titled(wb = wb, sheet = "Page2", c_title = c4_title, chart = "chart4_state.png", row = row_t07, col = 7)
add.chart.titled(wb = wb, sheet = "Page2", c_title = c7_title, chart = "chart7_state.png", row = 22, col = 7)

## add Page2's bottom border
addStyle(wb, sheet = "Page2", style = sBorder, rows = rows_page2, cols = 1:7, stack = TRUE)

## stretch cols and rows, freeze top rows
setColWidths(wb, sheet = "Page2", cols = 1:7, widths = c(6, 12, 12, 12, 12, 4, 66))
setRowHeights(wb, sheet = "Page2", rows = c(3:rows_page2), heights = 14) ## set heights
setRowHeights(wb, sheet = "Page2", rows = rows_title_p2, heights = 29)   ## title rows
setRowHeights(wb, sheet = "Page2", rows = rows_headers_p2, heights = 29) ## table header rows
setRowHeights(wb, sheet = "Page2", rows = rows_source_p2, heights = 11)  ## source rows
setRowHeights(wb, sheet = "Page2", rows = rows_blank_p2, heights = 11)   ## blank rows
freezePane(wb, sheet = "Page2", firstActiveRow = 3, firstActiveCol = 1)


### * save workbook ----
saveWorkbook(wb, paste0("Fact", params$state, ".xlsx"), overwrite = TRUE)
## Copy the report file to a temporary directory before processing it, in case we don't have write permissions to the current working dir (which can happen when deployed).
tempWB <- file.path(tempdir(), paste0("Fact", params$state, ".xlsx"))
file.copy(from = paste0("Fact", params$state, ".xlsx"), to = tempWB, overwrite = TRUE)
rm(wb, i)

```
